Whole-body connectome of a segmented annelid larva

### 2025-07-15 README.Rmd
Readme update and biorxiv pdf version uploaded
update README and CITATION with general Zenodo DOI citing all versions

[![DOI](https://zenodo.org/badge/773035678.svg)](https://zenodo.org/doi/10.5281/zenodo.10825370)

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, Gáspár Jékely (2024)
 \. _`r Title`_.  biorxiv. Online at <https://doi.org/10.1101/2024.03.17.585258>

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, , Gáspár Jékely, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://zenodo.org/records/11811680>

@@

  - [:file\_folder: text](Manuscript.qmd): Quarto source document
    for manuscript. Includes text, references and inserts the latest version of the figures from the /Figures folder. 
There is also a rendered html version,
    `Manuscript.html`, suitable for reading.

  - [:file\_folder: data](/data): Data used in the analysis.
  - [:file\_folder: scripts](/code): scripts used in the analysis.
  - [:file\_folder: images](/pictures): Plots and other
    illustrations  
  - [:file\_folder: figures](/Figures): All figures for the paper
  - [:file\_folder: supplements](/supplements):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder: source_data](/source_data):
    Source data files associated with each figure containing all data points that have been plotted in the figure.

>>>>

[![DOI](https://zenodo.org/badge/773035678.svg)](https://doi.org/10.5281/zenodo.10825370)

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, Gáspár Jékely (2024)
 \. _`r Title`_.  eLife Online at <https://elifesciences.org/reviewed-preprints/97964>

@@

> Csaba Verasztó, Sanja Jasek, Martin Gühmann, Luis Alberto Bezares Calderón, Elizabeth A. Williams, Réza Shahidi, , Gáspár Jékely, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.10825370>

@@

  - [:file\_folder: text](Manuscript.qmd): Quarto source document
    for manuscript. Includes text, references and inserts the latest version of the figures from the /Figures folder. 
The quarto file can be rendered into an html or pdf file in RStudio with all figures inserted, suitable for reading. For this, you need to download the repository, as explained below.

  - [:file\_folder: data](/data): Data used in the analysis.
  - [:file\_folder: scripts](/code): scripts used in the analysis.
  - [:file\_folder: images](/pictures): Plots and other
    illustrations  
  - [:file\_folder: figures](/Figures): All figures for the paper
  - [:file\_folder: supplements](/supplements):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder: source_data](/source_data):
    Source data files associated with each figure containing all 
    data points that have been plotted in the figure.
  - [:file\_folder: videos](/Videos):
    Videos in mp4 format.
